taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-03-10 paper/manuscript.Rmd

```{r}
iucn_ids <- unmatched$species %>% ids("iucn") %>% select(acceptedNameUsageID) %>% distinct()
right_join(taxa_tbl("iucn"), iucn_ids, copy=TRUE, by ="acceptedNameUsageID") %>% 
  select(scientificName, taxonomicStatus, acceptedNameUsageID, taxonRank, taxonID)
```

@@

```{r}
descendants(id = x$ott_id, provider = "ott") %>% select(scientificName, taxonomicStatus, acceptedNameUsageID)
```

@@

```{r}
syn$synonym %>% na.omit() %>% ids("ott") %>% select(input, scientificName, acceptedNameUsageID, taxonomicStatus)
```

@@

```{r}
c("Trochilidae",  "Ardeidae") %>% ids("ott")
```

>>>>

```{r}
iucn_ids <- unmatched$species %>% by_name("iucn") %>% select(acceptedNameUsageID) %>% distinct()
right_join(taxa_tbl("iucn"), iucn_ids, copy=TRUE, by ="acceptedNameUsageID") %>% 
  select(scientificName, taxonomicStatus, acceptedNameUsageID, taxonRank, taxonID)
```

@@

```{r}
by_id(id = x$ott_id, provider = "ott") %>% select(scientificName, taxonomicStatus, acceptedNameUsageID)
```

@@

```{r}
syn$synonym %>% na.omit() %>% by_name("ott") %>% select(input, scientificName, acceptedNameUsageID, taxonomicStatus)
```

@@

```{r}
c("Trochilidae",  "Ardeidae") %>% by_name("ott")
```
